\texttt{compGeometeR}: an \texttt{R} package for computational geometry

### 2021-03-18 paper/main.tex
Updated code examples in the paper

\begin{lstlisting}[language=R, caption=Example \texttt{R} code to create a discrete convex hull with \texttt{compGeometeR}, label={code:discrete-convex-hull-code}]
library(compGeometeR)
# Generate point data
set.seed(2) # to reproduce figure exactly
x = rgamma(n = 20, shape = 3, scale = 2)
y = rnorm(n = 20, mean = 10, sd = 2)
p = cbind(x, y)
# Create convex hull
ch = convex_hull(p)
# Plot point data and convex hull
plot(x, y, yaxt="n", xaxt="n", xlab="", ylab = "", pch=16, cex=0.75)
polygon(ch$hull_vertices, col="orange", border="firebrick")
points(p, pch=16, cex=0.75)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Example \texttt{R} code to create a digital convex hull with \texttt{compGeometeR}, label={code:digital-convex-hull-code}]
library(compGeometeR)
# Generate point data
set.seed(2) # to reproduce figure exactly
x = rgamma(n = 20, shape = 3, scale = 2)
y = rnorm(n = 20, mean = 10, sd = 2)
p = cbind(x, y)
# Create digital convex hull
d_ch = digital_convex_hull(p, mins=c(0,5), maxs=c(15,15), spacings = c(0.05,0.05))
# Plot point data and digital convex hull
image(x=d_ch[[3]][[1]], y=d_ch[[3]][[2]], z=d_ch[[1]], 
      yaxt="n", xaxt="n", xlab="", ylab = "", col=c("white", "orange"))
points(p, pch=16, cex=0.75)
\end{lstlisting}

>>>>

\begin{lstlisting}[language=R, caption=Example \texttt{R} code to create a discrete convex hull (Figure \ref{fig:discrete-algorithms}a) with \texttt{compGeometeR}, label={code:discrete-convex-hull-code}]
library(compGeometeR)
# Generate point data
set.seed(2) # to reproduce figure exactly
x = rgamma(n = 20, shape = 3, scale = 2)
y = rnorm(n = 20, mean = 10, sd = 2)
p = cbind(x, y)
# Create convex hull
ch = convex_hull(p)
# Plot point data and convex hull
plot(x, y, yaxt="n", xaxt="n", xlab="", ylab = "", pch=16, cex=0.75)
polygon(ch$hull_vertices, col="orange", border="firebrick")
points(p, pch=16, cex=0.75)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, caption=Example \texttt{R} code to create a digital convex hull (Figure \ref{fig:digital-algorithms}a) with \texttt{compGeometeR}, label={code:digital-convex-hull-code}]
library(compGeometeR)
# Generate point data
set.seed(2) # to reproduce figure exactly
x = rgamma(n = 20, shape = 3, scale = 2)
y = rnorm(n = 20, mean = 10, sd = 2)
p = cbind(x, y)
# Create digital convex hull
d_ch = digital_convex_hull(p, mins=c(0,5), maxs=c(15,15), spacings = c(0.05,0.05))
# Unpack the digital convex hull components and plot
d_ch_array <- d_ch[[1]]
x_coords <- d_ch[[2]][[1]]
y_coords <- d_ch[[2]][[2]]
image(x=x_coords, y=y_coords, z=d_ch_array, 
      yaxt="n", xaxt="n", xlab="", ylab = "", col=c("white", "orange"))
points(p, pch=16, cex=0.75)
\end{lstlisting}
